---
title: "R Notebook"
output: html_notebook
---


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r}
library(httr)
```

```{r}
# This command gives table of content for the root  directory, listing uuids for all the groups
r= GET("http://127.0.0.1:5000?host=icmplus.neurosurg.cam.ac.uk")
str(content(r, "parsed"))
```


```{r}
# This command gives uuid's of gropus present inside our hdf file( icmdata.hdf5)
r= GET("http://127.0.0.1:5000/groups?host=icmdata.public.icmplus.neurosurg.cam.ac.uk")
str(content(r, "parsed"))
```


```{r}
# This command list all the databases inside our hdf file
r= GET("http://127.0.0.1:5000/datasets?host=icmdata.public.icmplus.neurosurg.cam.ac.uk")
str(content(r, "parsed"))
```
```{r}
# concatenated dataset using select parameter
r= GET("http://127.0.0.1:5000/datasets/5cd3702a-24c4-11e8-bc5e-4cbb5813b2f6/value?select=[1:10,1:11]&host=icmdata.public.icmplus.neurosurg.cam.ac.uk")
str(content(r, "parsed"))
```


```{r}
# This command obtain fetch all data from one of the datasets inside our hdf file using its uuid
r= GET("http://127.0.0.1:5000/datasets/5cd3702a-24c4-11e8-bc5e-4cbb5813b2f6/value?host=icmdata.public.icmplus.neurosurg.cam.ac.uk")
str(content(r, "parsed"))
```


